---
title: "ROSS lab Reservoir Study Data Sharing"
format: html
editor: visual
---

```{r}
#| label: load-packages
#| include: false

library(tidyverse)
library(downloadthis)
source("package_loader.R")
source("field_chemistry/00_colors_and_groups.R")

```

```{r}


reservoir_chemistry <- read_feather("data/field_chemistry/cleaned/reservoir_chem_2021_2022_062023.feather")%>%
  mutate(location = factor(location, levels = c("Inflow","Reservoir", "Outflow", "Stream", "Mainstem")))


```

# Data

## Data Available

The data available at this site is grab sample chemistry data collected and processed at the RMRS Biogeochemistry lab. The data available here has been QA/QC'd and should be treated as final data.

## Download data

Add Zenodo link here!!

<!-- ::: {.callout-note appearance="minimal"} -->
<!-- <i class="bi bi-download"></i> [Download CPF Reservoir Study Dataset (4/2021 - 6/2023) dataset](sharing_data/field_chemistry/cleaned/CPF_reservoir_chemistry_up_to_071023.csv){download="CPF_reservoir_chemistry_up_to_071023.csv"} -->
<!-- ::: -->

<!-- ::: {.callout-note appearance="minimal"} -->
<!-- <i class="bi bi-download"></i> [Download mean nutrients dataset](sharing_data/field_chemistry/cleaned/mean_nutrients_2021_2022.csv){download="CPF_Res_mean_nutrient_data.csv"} -->
<!-- ::: -->

# Plots

## Plot 1: Longitudinal view of Joe Wright Creek

```{r}
  
 
chambers_longitudinal_plotter <- function(res_data = reservoir_chemistry, chosen_dates){
  
   #chambers dataframe
  chambers_longitudinal <- res_data %>%
    dplyr::filter(!is.na(ChlA)) %>%
    dplyr::filter(site_code %in% c("JOEI", "JOER", "CBRR", "CBRI", "CHD")) %>%
    dplyr::filter(Date %in% chosen_dates)%>%
    mutate(Date=as.character(Date),
           location_type = ifelse(location == "Outflow"|location =="Inflow", "Stream", "Reservoir"))
  
  ###PLOTING PART OF FUNCTION
  
  #chla graph
  chambers_chla_long <- chambers_longitudinal%>%
    ggplot(aes(x=Distance, y=ChlA, color=Date)) +
    geom_point( aes(shape = location_type), size=8, alpha = .7) +
    geom_line(aes(x=Xdistance), linewidth=2, alpha = .7) +
    geom_point(aes(shape = location_type), size=8, alpha = .7) +
    scale_color_manual(values = season_color_vals)+
    scale_fill_manual(values = season_color_vals)+
    theme_bw(base_size=30) +
    labs(shape = "", color="") +
    theme(axis.text.x = element_blank(), 
          legend.text = element_text(size = 18)) +
    xlab("") +
    ylab("Chlorophyll a (μg/L)")
  
  #NO3 GRAPH
  chambers_no3_long <- chambers_longitudinal%>%
    ggplot(aes(x=Distance, y=NO3, color=Date)) +
    geom_point( aes(shape = location_type), size=8, alpha = .7) +
    geom_line(aes(x=Xdistance), linewidth=2, alpha = .7) +
    geom_point(aes(shape = location_type), size=8, alpha = .7) +
    scale_color_manual(values = season_color_vals)+
    scale_fill_manual(values = season_color_vals) +
    theme_bw(base_size=30) +
    theme(legend.text = element_text(size =18))+
    labs(shape = "", color="") +
    scale_x_discrete(labels=c("1 - JOEI" = "Above Joe Wright", "2 - JOER" = "", "3 - CBRI" = "Above Chambers",
                              "4 - CBRR" = "", "5 - CHD" = "Below Chambers")) +
    xlab("Longitudinal Profile") +
    ylab("NO3 (mg/L)")
  
  
 chambers_plot <- ggarrange(chambers_chla_long,chambers_no3_long, ncol=1, nrow=2, common.legend=T)
  
return(chambers_plot)
}
  
  choosen_dates_2023 <- as.Date(c("2023-06-15",
                  "2023-06-09",
                  "2023-05-24"))
   choosen_dates_2022 <- as.Date(c(#"2022-06-01",
            "2022-06-14",
            #"2022-07-05",
            "2022-07-26",
            "2022-08-16",
                #"2022-08-23", "2022-08-30","2022-09-06","2022-09-13", "2022-09-20",
                  "2022-09-27",
                  #"2022-10-04","2022-10-11",
                  "2022-10-18"
                  #"2022-10-25",#"2022-11-01" 
            ))

  chambers_long_2022 <- chambers_longitudinal_plotter(reservoir_chemistry, chosen_dates = choosen_dates_2022)
  chambers_long_2022
  chambers_long_2023 <- chambers_longitudinal_plotter(reservoir_chemistry, chosen_dates = choosen_dates_2023)
  chambers_long_2023
  
  
 

#ggsave('test_output/2022_2023_joer_cbrr_chla_no3_longitudinal.jpg', width=15.5, height=10, dpi = 300)

```

## Plot 2: Longitudinal view of Joe Wright Creek and the Mainstem CLP
