---
title: "ROSS lab Reservoir Study Data Sharing"
output:
  html_document: 
    toc:true
---

```{r setup, include=FALSE}



library(tidyverse)
library(downloadthis)
source("package_loader.R")
source("field_chemistry/00_colors_and_groups.R")
knitr::opts_chunk$set(echo = FALSE)

```

```{r load_data, include=FALSE}


reservoir_chemistry <- read_feather("data/field_chemistry/cleaned/reservoir_chem_2021_2022_062023.feather")%>%
  mutate(location = factor(location, levels = c("Inflow","Reservoir", "Outflow", "Stream", "Mainstem")))


```

# Data

## Data Available

The data available at this site is grab sample chemistry data collected and processed at the RMRS Biogeochemistry lab. The data available here has been QA/QC'd and should be treated as final data.

## Download data

Add Zenodo link here!!

<!-- ::: {.callout-note appearance="minimal"} -->

<!-- <i class="bi bi-download"></i> [Download CPF Reservoir Study Dataset (4/2021 - 6/2023) dataset](sharing_data/field_chemistry/cleaned/CPF_reservoir_chemistry_up_to_071023.csv){download="CPF_reservoir_chemistry_up_to_071023.csv"} -->

<!-- ::: -->

<!-- ::: {.callout-note appearance="minimal"} -->

<!-- <i class="bi bi-download"></i> [Download mean nutrients dataset](sharing_data/field_chemistry/cleaned/mean_nutrients_2021_2022.csv){download="CPF_Res_mean_nutrient_data.csv"} -->

<!-- ::: -->

# Plots

## Plot 1: Longitudinal View of NO3 and chlorophyll-a in Joe Wright Creek through Joe Wright Reservoir and Chambers Lake

### Selected Dates of 2022
```{r 2022 JWC Plot, fig.align='center', fig.width=15.5, fig.height=10}
source("jwc_long_plotter.R")
  
   choosen_dates_2022 <- as.Date(c(#"2022-06-01",
            "2022-06-14",
            #"2022-07-05",
            "2022-07-26",
            "2022-08-16",
                #"2022-08-23", "2022-08-30","2022-09-06","2022-09-13", "2022-09-20",
                  "2022-09-27",
                  #"2022-10-04","2022-10-11",
                  "2022-10-18"
                  #"2022-10-25",#"2022-11-01" 
            ))

  chambers_long_2022 <- chambers_longitudinal_plotter(reservoir_chemistry, chosen_dates = choosen_dates_2022)
  chambers_long_2022
```

### Selected Dates of 2023
```{r 2023 JWC Plot, fig.align='center', fig.width=15.5, fig.height=10}
choosen_dates_2023 <- as.Date(c("2023-06-15",
                  "2023-06-09",
                  "2023-05-24"))
  
  chambers_long_2023 <- chambers_longitudinal_plotter(reservoir_chemistry, chosen_dates = choosen_dates_2023)
  chambers_long_2023


#ggsave('test_output/2022_2023_joer_cbrr_chla_no3_longitudinal.jpg', width=15.5, height=10, dpi = 300)

```

### 2022 and 2023 side by side

```{r side by side, fig.align='center', fig.width= 45, fig.height=20}

both <- ggarrange(chambers_long_2022, chambers_long_2023, ncol = 2, nrow = 1)
both
```


## Plot 2: Longitudinal view of Joe Wright Creek and the Mainstem CLP
